---
title: "p8105_hw1_yz4720"
author: "Jasmine Zhang"
date: "2023-09-23"
output: github_document
---

# Set up
```{r setup}
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

# Question 1
```{r Question1}
help(early_january_weather)
```
The dataset "early_january_weather" contains hourly weather data for LGA, JFK and EWR for the month of January 2013. There are 15 variables: origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. The size of the dataset is `r nrow(early_january_weather)` rows by `r ncol(early_january_weather)` columns. The mean temperature is `r mean(pull(early_january_weather,temp))`.

```{r plot}
scatterplot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
  geom_point()
scatterplot
ggsave(scatterplot, file="scatterplot_question1.pdf")
```
From the scatterplot, it can be noticed that temperature fluctuates during each day (increases during the day and decreases during the night). The overall temperature increases as days progress in January. In addition, it rained for the period around Jan 10th to 14th because the humidity increased a lot.

# Question 2
## Create the dataframe
```{r Question2}
q2_df = tibble(
  samp = rnorm(10, mean = 0, sd = 1),
  samp_pos = samp > 0,
  samp_char = c("My", "name", "is", "Jasmine", "Zhang", "and", "I", "am", "from", "Shanghai"),
  samp_fac = factor(c("head", "tail", "head", "neither","tail", "neither", "tail", "tail", "neither","tail"))
)
q2_df
```

## Taking mean of each variable
```{r}
mean(pull(q2_df, samp))
mean(pull(q2_df, samp_pos))
mean(pull(q2_df, samp_char))
mean(pull(q2_df, samp_fac))
```
When taking the mean of each variable, it works for the random sample from a standard Normal distribution and the logical vector. It doesn't work for the character and factor vectors.

## Converting variables
```{r eval = FALSE}
as.numeric(pull(q2_df, samp_pos))
as.numeric(pull(q2_df, samp_char))
as.numeric(pull(q2_df, samp_fac))
```
When trying to convert the logical, character, and factor variables to numeric variable, it works for logical variable (by converting FALSE to 0 and TRUE to 1), and factor variable (by assigning 1, 2, 3 to the three levels of factor respectively). The conversion doesn't work for the character variable. This explains that taking the mean of a logical variable was successful. But the mean function can only be applied to numeric or logical variables but not factor variable.
