---
title: "p8105_hw1_yz4720"
output: html_document
date: "2023-09-21"
---

# Set up
```{r setup}
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

# Question 1
```{r Question1}
help(early_january_weather)
```
In the dataset "early_january_weather", the variables are origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. The size of the dataset is `r nrow(early_january_weather)` rows by `r ncol(early_january_weather)` columns. The mean temperature is `r mean(pull(early_january_weather,temp))`.

```{r plot}
scatterplot<- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
  geom_point()
scatterplot
ggsave(scatterplot, file="scatterplot_question1.pdf")
```
From the scatterplot, it can be noticed that temperature fluctuates during each day (increases during the day and decreases during the night). The overall temperature increases as days pass progress in January. In addition, it rained for the period around Jan 10th to 14th because the humidity increased a lot.

# Question 2
## Create the dataframe
```{r Question2}
q2_df = tibble(
  samp = rnorm(10, mean = 0, sd = 1),
  samp_pos = samp > 0,
  samp_char = c("My","name","is","Jasmine","Zhang","and","I","am","from","Shanghai"),
  samp_fac = factor(c("head", "tail", "head", "neither","tail", "neither", "tail", "tail", "neither","tail"))
)
q2_df
```

## Taking mean of each variable
```{r}
mean(pull(q2_df, samp))
mean(pull(q2_df, samp_pos))
mean(pull(q2_df, samp_char))
mean(pull(q2_df, samp_fac))
```
When taking the mean of each variable, it works for the random sample from a standard Normal distribution and the logical vector. It doesn't work for the character and factor vectors.

## Converting variables
```{r eval = FALSE}
as.numeric(pull(q2_df, samp_pos))
as.numeric(pull(q2_df, samp_char))
as.numeric(pull(q2_df, samp_fac))
```
When trying to convert the logical, character, and factor variables to numeric variable, it works for logical variable (by converting FALSE to 0 and TRUE to 1), and factor variable (by assigning 1, 2, 3 to the three levels of factor respectively). The conversion doesn't work for the character variable. This explains that taking the mean of a logical variable was successful. But the mean function can only be applied to numeric or logical but not factor.
